---
output:
  pdf_document: default
  html_document: default
---

<!-- saved from url=(0100)https://moodle-1819.ucl.ac.uk/pluginfile.php/1342515/mod_resource/content/7/stat0017ica1template.Rmd -->
<html><head><meta http-equiv="Content-Type" content="text/html; charset=UTF-8"></head><body>---
title: "STAT0017 ICA 1 2018-19"
author: "Student number: 17052480"
date: "`r Sys.Date()`"
output:
  rmarkdown::pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    fig_width: 6
    fig_height: 4
---

```{r, include = FALSE}
# Load the data (you will need to edit this to point to the correct directory
# on your computer)
setwd("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1")
load("wm.Rdata")
load("pot.Rdata")
# You will also need to load any R libraries that you want to use.
library("evd")
library("evdbayes")
library("ismev")
library("revdbayes")
library("threshr")
library("bayesplot")
library("coda")
source("/Users/hongwei/Documents/GitHub/STAT/STAT0017_ICA1/pjnfunctions.R")
# Some parts of the analyses are based on simulation.
# We set a set a random number seed so that
# 1. The numeric results on which you comments will not change each time you run
#    your code (unless you change the order of the analyses)
# 2. Your work is easier for me to mark.
#### PLEASE DO NOT CHANGE THE FOLLOWING LINE OF CODE (KEEP THE SEED as 17) ####
set.seed(17)
```

---
# [This is a comment block that will not appear in your PDF file]
# Add your text (perhaps with LaTeX code in it) and R code in the 
# relevant sections below.
# There is an example of an R code `chunk' in the Winter maxima (wm) section
---

# Extremal Types Example

${}$\hspace*{\fill} [25] 

---
# You could put LaTeX code into this section to give your answer to Part A.
# You can only use basic LaTeX code (no extra packages).
# If you don't do this then please don't delete the Extremal Types Example
# heading above: just leave this section blank.
---

## Question 1 (a)
From the question we can see:
$$ F(x)= P(X \leq x)= \begin{cases} 1-e^{1/x}, & \text {for $x < 0$ .} \\ 1, & \text{for $x \geq 0$ .} \end{cases} \tag {*}$$
$$ M_n=max \lbrace x_1,...,x_n \rbrace $$ 
Hazard Function:
\begin{align}
h(x) & =\frac{1-F(x)}{f(x)} \\
  & = \frac{e^{1/x}}{e^{1/x} \times (-x^{-2})} \\
  & =-x^{2}
\end{align} 
Derivative of h(x):
$h^{'}= -2x$

\begin{align}
\lim_{x \to x^F} h^{'}(x) \to \xi \\
Let\ \xi = -2M_n \\
We\ can\ see:\  x \sim GEV(0,1,-2M_n)
\end{align} 

From the slides we have:
$$\begin{cases} 1-F(b_n)=1/n \\ a_n=h(b_n) \end{cases}$$
solve it we have: 
$$\begin{cases} b_n=- \frac{1}{log(n)} \\ a_n=- \frac{1}{{log^2(n)}} \end{cases}$$

## Question 1 (b)
When $\xi < 0$ the GEV distribution has light upper tail with the finite upper limit which is  $\mu - \sigma / \xi$. 
  
Let $\mu - \sigma / \xi = 0$ then this distribution with a finite upper end point of 0  has an upper end point of infinity.

## Question 1 (c)
We assume $A = \{ x: 0< F(x)<1 \}$ , and $x^*=sup_{x \in A} A$. 
  
Here F(x) can be any function including the function $(*)$.
    
For $\forall x, x<x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 0, as \  n \to \infty$.
 
For $\forall x, x \geq x^*$, we have $Pr(M_n \leq x)=F^n(x) \to 1 , as \ n \to \infty$.
  
This is mean whatever x or F(x), $M_n = 0 or 1$ when $n \to \infty$. 
  
The $M_n$ is Degenerate distribution, which is useless. 
  
That is why we need fit a GEV model.

## Question 1 (d)
The log-likelihood:
$$\xi_n \approx h^{'}(x)|_x=u(n) \ where \ u(n)=F^{-1}(1-1/n)$$
Thus $$\xi= h^{'}(x) = -2/ln(365) = -0.3400$$



# Exploratory analysis

## Winter maxima (wm)

```{r}
# Add R code here (and similarly elsewhere)
plot(wm$waterYear,wm$Hs,bty="l",pch=20,xlab="year",ylab="wave height (in metres)")
#(wm$Hs~wm$meanNAO) 
plot(wm$meanNAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the mean of NAO")
abline(lm(wm$Hs~wm$meanNAO), col="red") # regression line (wm$Hs~wm$meanNAO) 
lines(lowess(wm$Hs~wm$meanNAO), col="blue") # lowess line (wm$Hs~wm$meanNAO)
#(wm$Hs~wm$maxNAO)
plot(wm$maxNAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the max of NAO")
abline(lm(wm$Hs~wm$maxNAO), col="red") # regression line (wm$Hs~wm$maxNAO)
lines(lowess(wm$Hs~wm$maxNAO), col="blue") # lowess line (wm$Hs~wm$maxNAO)
#(wm$Hs~wm$meanA0)
plot(wm$meanA0,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the mean of AO")
abline(lm(wm$Hs~wm$meanA0), col="red") # regression line (wm$Hs~wm$meanA0)
lines(lowess(wm$Hs~wm$meanA0), col="blue") # lowess line (wm$Hs~wm$meanA0)
#(wm$Hs~wm$maxAO)
plot(wm$maxAO,wm$Hs,bty="l",pch=20,xlab="wave height (in metres)",ylab="the max of AO")
abline(lm(wm$Hs~wm$maxAO), col="red") # regression line (wm$Hs~wm$maxAO)
lines(lowess(wm$Hs~wm$maxAO), col="blue") # lowess line (wm$Hs~wm$maxAO)


```

## Storm peaks (pot)
```{r}
plot(pot$date,pot$Hs,bty="l",pch=20,xlab="date",ylab="wave height (in metres)")
```

## Comments
The relationship between wave height and all of variables can be roughly seen through the scatter plot. As can be seen from the line graph, the more the red line coincides with the blue line, the better the linear regression model fits. As can be seen from the plot, the average of AO has a better fitting relationship with the height of the waves. Further analysis needs to be carried out, followed by analysis.
${}$\hspace*{\fill} [10]

# Extreme value (EV) modelling of $H_s$

## GEV modelling of winter maxima
```{r}
wm.gev <- gev.fit(wm[,1])#fit GEV model
wm.gev$mle#GEV MLEs
wm.gev$se#standard errors of MLEs
pjn.gev.diag(wm.gev) #PJN's GEV diagnostics
```

### Maximum Likelihood-Based Inference
```{r}
pjn.gev.conf(wm.gev, conf = 0.95)
pjn.gev.profxi(wm.gev, -1, 1, conf = 0.95)   
pjn.gev.conf.ret.levels(wm.gev, m = 100, conf = 0.95)
# Profile log-likelihood for the 100 year return level
pjn.gev.prof(wm.gev,m=100,14,20)# PJN's version
```

### Comments

First, the model is fitted, and the three parameters of the model are 11.2726903,  1.2064985, -0.1534719 respectively. Their variances are 0.18140907, 0.12880447, 0.09956538 respectively. Through the diagnosis, we can see that the tail of data is basically appropriate, and it can be seen the model's trend.

### Bayesian Inference
```{r}
my.ylab <- c("mu","sigma","xi")
# Set independent normal priors with large variances 
prior.cov.mat <- diag(c(10000, 10000, 100))         
pn <- prior.norm(mean = c(0, 0, 0), cov = prior.cov.mat) 

# Starting well away from the MLEs
init <- c(11,1,0.1)                
# SDs of the proposal distributions for (mu, ln(sigma), xi)
prop.sd <- c(0.18,0.12,0.1)       
prop.sd.auto <- ar.choice(init = init, prior = pn, lh = "gev", 
                          data = wm$Hs, psd = prop.sd, 
                          tol = rep(0.02, 3))$psd
post <- posterior(3000, init = init, prior = pn, lh = "gev", 
                  data = wm$Hs, psd = prop.sd.auto)
for (i in 1:3) plot(post[,i],ylab=my.ylab[i]) 
attr(post,"ar")        
# Posterior dependence among parameters
pairs(post)
```

### Comments
Bayesian Inference

## Binomial-GP modelling of storm peaks
```{r}
pot.gp <- gpd.fit(pot[,1], 10)
```

### Threshold selection
```{r}
mrl.plot(pot[,1])
# PJN's GP diagnostics 
pjn.gpd.diag(pot.gp)    
```

### Maximum Likelihood-Based Inference
```{r}
#Symmetric 100*conf% confidence intervals for p_u, sigma_u and xi 
pjn.gpd.conf(pot.gp, conf = 0.95)
#PJN's version of ismev::gpd.profxi 
pjn.gpd.profxi(pot.gp, xlow = -0.3, xup = 0.2, conf = 0.95) 
#Symmetric 100*conf% confidence intervals for the 100-year return level 
pjn.gpd.conf.ret.levels(pot.gp, m = 100, npy = 10, conf = 0.95)
#Profile log-likelihood for the 100-year return level 
pjn.gpd.prof(pot.gp, m = 100, xlow = 14, xup = 20, npy = 10, conf = 0.95) 
```

### Comments

The estimated of $\xi$ is -0.15, and the corresponding 95% confidence interval is [-0.33,0.07].

### Bayesian Inference
```{r}
fp <- set_prior(prior = "flat", model = "gp", min_xi = -1)
bp <- set_bin_prior(prior = "jeffreys")
u <- quantile(pot[,1], probs = 0.8)
bgpg <- rpost(n = 10000, model = "bingp", prior = fp, thresh = u, data = pot[,1],
              bin_prior = bp, npy = 10)
plot(bgpg, pu_only = TRUE)
plot(bgpg, add_pu = FALSE)
plot(bgpg, add_pu = TRUE)

```

### Comments

It can also be seen that the likelihood function of the 100 year return level. It takes a constant attempt to return the plot to find th likelihood function is asymmetrical, the confidence interval is also asymmetrical with respect to the maximum likelihood estimate. 
${}$\hspace*{\fill} [25]

## Reporting to your client

From the plot we can see that the return period is 100. The estimated level of reconstruction for the year is 15.25, and the corresponding 95% confidence interval is [14.42,17.7].

${}$\hspace*{\fill} [15]

# EV regression modelling of winter maximum $H_s$ on NAO

## Build a GEV regression model

${}$\hspace*{\fill} [15]
```{r}

evd_fit0 <- fgev(wm[,1])
covaryear <- data.frame(scaled_year = (wm[,2]-1955)/(2010-1955))
covar2 <- data.frame(scaled_year = (wm[,2]-1955)/(2010-1955), NOA = wm[, 3])
evd_fit1 <- fgev(wm[,1], nsloc = covaryear)
evd_fit2 <- fgev(wm[,1], nsloc = covar2)

anova(evd_fit2, evd_fit1, evd_fit0)

fitted(evd_fit2) # strictly speaking this should be coef() 
std.errors(evd_fit2)
vcov(evd_fit2)
confint(evd_fit2)
plot(evd_fit2)
```

## Inference for $H_s^{100}$

${}$\hspace*{\fill} [10]

<script type="text/x-mathjax-config">
   MathJax.Hub.Config({  "HTML-CSS": { minScaleAdjust: 125, availableFonts: [] }  });
</script>
</body></html>